Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-25 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:25	14:02:29	(Fri25.Sep)

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{One of the objects used to test the beamformers is a 1\,m long cross attached to an anchor with a diameter of $\approx$13\,cm.}\label{cross}
\end{figure}

>>>>

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross_tagged.png}%
\caption{One of the objects used to test the beamformers is a 1\,m long cross attached to an anchor with a diameter of approximately 13\,cm.}\label{cross}
\end{figure}
